\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-13 WOOT/Files/background.tex
add impl part, todo: three mode
Add introduction

\section{Background}
\label{sec:background}
\noindent\outline{USB Standard}\\
We first introduce the development of USB specification and emphasize the key points adopted in our work.

@@

\noindent\outline{Security Problem}\\
During the development of USB specification, security was rarely considered.  As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}. But the divergent implementations give chance for attack like Rubber Ducky\cite{rubber} and our \tool.

>>>>

\section{Background}
\label{sec:background}
\shuqing{Maybe we could introduce HID devices somewhere.}
\noindent\outline{USB Standard}\\
We first introduce the development of USB specification and emphasize the key points adopted in our work. We also organized a brief timeline introducing key points of each protocol in Table~\ref{table:usb_timeline}.

@@

\noindent\outline{Security Problem}\\
During the development of USB specification, security was rarely considered.  As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}. But the divergent implementations give a chance for attack like Rubber Ducky\cite{rubber} and our \tool.
\begin{table*}
\begin{tabular}{|c|c|c|c|c|}
	\hline
	Year & Protocol Version & Supported Peripherals & Transfer Speed & Attacks \\
	\hline
	1996 & USB 1.x & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating(BadUSB) \\
	\hline
	2000 & USB 2.0 & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack, Juice Filming Attack \\
	\hline
	2008 & USB 3.0 & / & 5 Gbit/s & / \\
	\hline
	2013 & USB 3.1 & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & Armory \\
	\hline
	2017 & USB 3.2 & / & 20 Gbit/s & / \\
	\hline
\end{tabular}
	\linebreak
\caption{USB Protocol Timeline}
\label{table:usb_timeline}
\end{table*}

### 2021-01-13 WOOT/Files/badusb.tex
Update comments

\section{\tool}
\label{sec:badusb}
\subsection{Motivation}
\noindent\outline{Limitation of Rubber Ducky}\\
\outline{Our functionality different mode listing?}\\
\hongyi{The following mode is to be further decided}
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend normal HID devices and utilize USB protocol to perform attacks. 
However, these attacks suffer from various drawbacks:
\ding{182} attackers can only simulate limited types of devices such as HIDs (like keyboards and mice) and disks, which makes the attacks less effective;
\ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to locate their attacks precisely or confirm the effects after attacks.

@@

\subsubsection{Hardware Specification}
The hardware we use is as follows and the relation between them is illustrated at Fig.~\ref{fig:hardware_specification}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by Raspberry Pi.
	\item\textit{Raspberry Pi} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
	\item\textit{Rubber Ducky} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
\end{itemize}
\begin{figure}[hbtp]
	\includegraphics[width=\linewidth]{./Figs/hardware_specification.png}
	\caption{Hardware Specification}
	\label{fig:hardware_specification}
\end{figure}
\textbf{Scripting Mode}
\tool under this mode works almost the same like the original Rubber Ducky with various improvement.

@@

This mode enable attacker to perform delicate operation that is beyond automation. Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by firewall running on the host machine.
\hongyi{I think this is a quite good selling point?}

>>>>

\section{\tool}
\label{sec:badusb}
\subsection{Threat Model}
We build our threat model on the basic assumptions that common users without technical background would not treat normal-looking USB device as highly dangerous and be cautious about them. These assumptions are approved in a relevant work about charging attack\cite{JFCImpact}. Moreover, we neglect the effect of notification about common USB device, as normal users usually are not equipped with the necessary knowledge to fully understand such notices. In fact, during our experiment, no device had security notifications raised about suspicious USB devices and only mobile devices had raised charging notification about our \tool, which is not a sufficient warning towards users.

We also assume the victim's device is equipped with fully functional USB 3.x protocol and USB Type C connector. As the USB 3.x standard is more and more common around the world, this assumption can be easily fulfilled especially in recent devices.
\subsection{Motivation}
\noindent\outline{Limitation of Rubber Ducky}\\
\outline{Our functionality different mode listing?}\\
\hongyi{The following mode is to be further decided}
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend normal HID devices and utilize USB protocol to perform attacks. 
However, these attacks suffer from various drawbacks:
\ding{182} attackers can only simulate limited types of devices such as HIDs (like keyboards and mice) and disks, which makes the attacks less effective;
\ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to locate their attacks precisely or confirm the effects after attacks.

@@

\subsubsection{Attack Model}
The components in our attack model are as follows and the relation between them is illustrated at Fig.~\ref{fig:attack_model}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by Raspberry Pi.
	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
	\item\textit{HID Emulator} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
\end{itemize}
\begin{figure}[hbtp]
	\includegraphics[width=\linewidth]{./Figs/attack_model.png}
	\caption{Attack Model}
	\label{fig:attack_model}
\end{figure}
\textbf{Scripting Mode}
\tool under this mode works almost the same like the original Rubber Ducky with various improvement.

@@

This mode enable attacker to perform delicate operation that is beyond automation. Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by firewall running on the host machine.
\hongyi{I think this is a quite good selling point?}\shuqing{Agree with Hongyi.}
